County Figures

### 2023-07-03 reports/county_figures.Rmd
update figures

filter_versions <- FALSE 
save_figures <- FALSE

@@

@@

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  
               label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Mean Wastewater Concentration")

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "")

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Mean Wastewater Concentration")

plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County by County)",
       title = "")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County by County)",
       y = "Covidestim Estimates\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County by County)",
       y = "Covidestim Estimates\n(Standardized by County by County)",
       title = "")

@@

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
    "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
    "Priors Do Not Vary by County and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

@@

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County by County)",
       y = "Wastewater Concentrations\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

@@

For each county, normalize the wastewater concentration by the maximum concentration for that county and the probabilistic bias counts by the maximum *median* estimated counts for that county (2.5th percentile and 97.5th percentile also standardized by the maximum *median* estimated counts for that county).

@@

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Mean Wastewater Concentration")

plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "")
```

@@

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

@@

county_dat <- county %>%
  # set Nantucket, Duke fips to Nantucket since we have wastewater data
  # for Nantucket
  left_join(dates,  relationship = "many-to-many") %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate = max(date)) %>%
  ungroup() %>%
  left_join(county_names, by=c('fips'='fips')) %>%
  left_join(versions) %>%
  mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name))

county_dat %>%
  filter(version=="v7")  %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_wrap(~name, scales="free_y", ncol=3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
    axis.text.x=element_text(size=7),
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

county_dat %>%
  filter(fips %in% sample(unique(.data$fips),2))  %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

county_dat %>%
  filter(version=="v7")  %>%
  #filter(grepl("Nan",name)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb/positive,
             ymax = exp_cases_ub/positive),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   # geom_linerange(aes(xmin = mindate,
   #                    xmax=maxdate,
   #                    y = positive,
   #                    color = 'obs')) +
  facet_wrap(~name,ncol=3) +
 # facet_grid(name~vlabel, 
 #                 labeller=labeller(vlabel =as_labeller(
 #                   TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top") +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Ratio of Estimated to Observed Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

############################################
# POSITIVE TESTS AND TEST POSITIVITY
############################################
pltlist <- county_dat %>%filter(version=="v7") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(testpos)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=testpos*adj, color='Test Positivity'),
              linetype=2) +
      geom_point(aes(y=testpos*adj, color='Test Positivity'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Test Positivity"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2),
                                                    linewidth=c(2,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=10),
          axis.text =element_text(size=9),
          legend.position="none") +
    scale_y_continuous(labels=comma, sec.axis = sec_axis(~./adj , name = 'Test Positivity')) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)

@@

# Summary of Comparison Between Implementations

>>>>

filter_versions <- TRUE 
save_figures <- TRUE

@@

if(filter_versions) {

  county <- county %>%
    left_join(versions) %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      TRUE ~ vlabel
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    left_join(county_names) %>%
    mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name)) %>%
    left_join(dates,  relationship = "many-to-many") %>%
    group_by(biweek) %>%
    mutate(mindate = min(date),
           maxdate = max(date)) %>%
    ungroup()

@@

correlations <- w_data %>%
  group_by(version) %>%
  summarize(Correlation = cor(exp_cases_median_std,mean_conc_std),
            vlabel =unique(vlabel)) %>%
  mutate(x=2.8,
         y=.1)

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  
               label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Mean Wastewater Concentration")

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations with Wastewater Concentrations")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations with Covidestim Infections")

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Mean Wastewater Concentration")

plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County by County)",
       title = "")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County by County)",
       y = "Covidestim Estimates\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County by County)",
       y = "Covidestim Estimates\n(Standardized by County by County)",
       title = "")

@@

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
    "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "Priors Do Not Vary by County and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

@@

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County by County)",
       y = "Wastewater Concentrations\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Covidestim Estimates")

@@

For each county, normalize the wastewater concentration by the maximum concentration for that county and the Probabilistic Bias Infections by the maximum *median* estimated counts for that county (2.5th percentile and 97.5th percentile also standardized by the maximum *median* estimated counts for that county).

@@

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Mean Wastewater Concentration")

plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "")

@@

w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Covidestim Estimates")

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "")
```

@@

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Covidestim Estimates")

@@

county %>%
  filter(version=="v7")  %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_wrap(~name, scales="free_y", ncol=3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
    axis.text.x=element_text(size=7),
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

county %>%
  filter(fips %in% sample(unique(.data$fips),2))  %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

county %>%
  filter(version=="v7")  %>%
  #filter(grepl("Nan",name)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb/positive,
             ymax = exp_cases_ub/positive),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   # geom_linerange(aes(xmin = mindate,
   #                    xmax=maxdate,
   #                    y = positive,
   #                    color = 'obs')) +
  facet_wrap(~name,ncol=3) +
 # facet_grid(name~vlabel, 
 #                 labeller=labeller(vlabel =as_labeller(
 #                   TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top") +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Ratio of Estimated to Observed Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

############################################
# POSITIVE TESTS AND TEST POSITIVITY
############################################
pltlist <- county %>%filter(version=="v7") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(testpos)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=testpos*adj, color='Test Positivity'),
              linetype=2) +
      geom_point(aes(y=testpos*adj, color='Test Positivity'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Test Positivity"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2),
                                                    linewidth=c(2,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=10),
          axis.text =element_text(size=9),
          legend.position="none") +
    scale_y_continuous(labels=comma, sec.axis = sec_axis(~./adj , name = 'Test Positivity')) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)

@@

# Faceted by Version

```{r, fig.width=15, fig.height=16}
